---
title: "Mind the age gap: age-mixing patterns predict HIV incidence"
output: html_notebook
---

### What are the key features of real life that the model should capture?
#### Age-mixing
1. WSD of age gaps
2. BSD of age gaps
3. slope
4. intercept

Important question: should we only have “general population” targets, or also hiv-status and gender specific targets? For now, only general male population.
 
#### Sexual activity:
Degree distribution of new sex partners in the last year:
5. shape parameter (r) of the negative binomial distribution = 1.29
6. scale parameter (theta) of the negative binomial distribution = 0.66 (theta = p/(1-p))
(For now we are not taking age effect into account, but if we were, e.g. via GAMM or other multi-parameter model): Extract age effect: Fitting NB distribution to data on number of new relationships in last year, with age covariate.
```{r nb.params}
library(dplyr)
library(MASS)
library(splines)
library(boot)
library(haven)
library(ggplot2)
library(fitdistrplus)
library(lmtest)

root.path <- dirname(getwd())

relations.data.path <- paste0(root.path, "/MiceABC/Sex Network Master (participant level) 09.08.2012.dta")

data.relations <- read_dta(file = relations.data.path)
#names(data.relations)
data.needed <- dplyr::select(data.relations, c(id,
                                     age,
                                     race,
                                     gender,
                                     cpcount,
                                     ompcount,
                                     hivtestresult,
                                     totalpartners))
data.needed$cpcount[is.na(data.needed$cpcount)] <- 0
data.needed$ompcount[is.na(data.needed$ompcount)] <- 0

#########################################################################################
# data.filtered is the dataset for the partner turnover analysis

data.filtered <- dplyr::filter(data.needed,
                               race == 2,
                               gender != "2",
                               age >= 15,
                               age < 50)

data.filtered$totalpartnerslstyr <- data.filtered$cpcount +
  data.filtered$ompcount # Total NEW relationships formed in the last year

data.filtered$age0 <- data.filtered$age - min(data.filtered$age)

# We create 4 subsets, one for each race-gender stratum
md.wideBM <- dplyr::filter(data.filtered,
                           race == 2,
                           gender == "0")    # Let's ONLY WORK WITH THIS STRATUM

md.wideBW <- dplyr::filter(data.filtered,
                           race == 2,
                           gender == "1")

###################################
#Negative binomial model
###################################
# Model for black men in the last year
intercept.Bm <- glm.nb(totalpartnerslstyr~1,
                       data = md.wideBM,
                       control = glm.control(maxit = 100000, trace = 3),
                       init.theta = 1)
summary(intercept.Bm) # intercept exp(0.25), theta = 0.65
shape.nb <- exp(as.numeric(intercept.Bm$coefficients)) #(r)
scale.nb <- as.numeric(intercept.Bm$theta) #(theta = p/(1-p))

# Or alternatively we can fit the negative binomial like this:
fit.negbin <- fitdist(as.numeric(md.wideBM$totalpartnerslstyr), "nbinom")

fit.pois <- fitdist(as.numeric(md.wideBM$totalpartnerslstyr), "pois")
r.pois <- rpois(n = 1000000, lambda = as.numeric(fit.pois$estimate))


# A negative binomial distribution is the result of gamma-distributed Poisson processes.
r.lambdas <- rgamma(n = 1000000, shape = shape.nb, scale = scale.nb)
r.negbinom <- rpois(n = length(r.lambdas), lambda = r.lambdas)
random.nb <- rnbinom(n = 10000, size = shape.nb, mu = shape.nb * scale.nb)

hist(md.wideBM$totalpartnerslstyr)
hist(r.negbinom)
hist(random.nb)
mean(md.wideBM$totalpartnerslstyr)
mean(r.negbinom)
mean(random.nb)

round(prop.table(table(as.numeric(md.wideBM$totalpartnerslstyr))), 2)
round(prop.table(table(random.nb)), 2)
round(prop.table(table(r.negbinom)), 2)
round(prop.table(table(r.pois)), 2)


finalBm <- glm.nb(totalpartnerslstyr~ns(age0, 3),
                data=md.wideBM,
                control=glm.control(maxit=100000, trace = 3),
                init.theta=0.5)

summary(finalBm)

lrtest(intercept.Bm, finalBm)

###############################################################################
# Made up data set to predict the expected number of sexual partners per age
##############################################################################
madeforBM <- data.frame(age0 = 0:34, gender = "man", race = "African") # ~ 15 to 49 year old men

madeforBM$totalpartnerslstyr <- NA
########################################################################################
tryBM <- predict(finalBm, newdata=madeforBM, type="link", se.fit = TRUE)
madeforBM$try <- exp(tryBM$fit);
madeforBM$try.low <- exp(tryBM$fit - 1.96 * tryBM$se.fit);
madeforBM$try.high <- exp(tryBM$fit + 1.96 * tryBM$se.fit);


### Final step: plotting the results
plot(seq(15, 49), madeforBM$try, type="l", col="navyblue",main="Black men",xlab="Age",ylab="Partnerslastyear", ylim = c(0, 4))
#points(seq(15, 49), madeforBM$try.low, col="navyblue")
#points(seq(15, 49), madeforBM$try.high, col="navyblue")

```

7. Concurrency: Beauclair JIAS 2015:Point-prevalence of concurrent partnerships 6 months before survey was 13.4% among black men

#### Epidemic trajectory
HIV prevalence by age and gender, by age-groups in 2011 (30 years after introducing HIV) as per Beauclair 2017 (journal unknown yet)
8. HIV prevalence in women < 25 yo: 0.2
9. HIV prevalence in men < 25 yo: 0.1
10. HIV prevalence in women 25 <= x < 35: 0.42
11. HIV prevalence in men 25 <= x < 35: 0.17
12. HIV prevalence in women 35 <= x < 45: 0.37
13. HIV prevalence in men 35 <= x < 45: 0.24

```{r define.summary.statistics}
wsd.general <- 3
bsd.general <- 1.5
slope.general <- 0.7
intercept.general <- -1 # average age of partners of 15 year-old boys is 16
shape.nb <- 1.29
scale.nb <- 0.66
pp.cp.6months.men <- 0.134
hiv.prev.lt25.women <- 0.2
hiv.prev.lt25.men <- 0.1
hiv.prev.25.34.women <- 0.42
hiv.prev.25.34.men <- 0.17
hiv.prev.35.44.women <- 0.37
hiv.prev.35.44.men <- 0.24

```


```{r define.wrapper.function, echo = FALSE}

library(devtools)
#install_github("wdelva/RSimpactHelp")
library(RSimpactCyan)
library(RSimpactHelper)
library(ggplot2)
library(GGally)
library(lmtest)
library(mice)
library(miceadds)
library(parallel)
library(randtoolbox)
library(EasyABC)
library(dplyr)
library(tidyr)
library(nlme)
library(lme4)
library(boot)
library(data.table)


# Let's create a colour palette that is colourblind-friendly
# The palette with black:
cb.Palette <- c("#F0E442", "#D55E00", "#0072B2", "#E69F00", "#999999")
#                yellow      red         blue     orange      grey



# First we define a simpact wrapper function that takes as argument a vector of model parameter values and returns a vector of summary statistics



# A wrapper function to run Simpact once
# input.vector <- c(0, 3, -0.5, 0)
simpact.wrapper.master <- function(inputvector = input.vector){
  library(RSimpactHelper)
  library(RSimpactCyan)
  library(magrittr)
  library(dplyr)
  library(nlme)
  
  agemixing.lme.errFunction <- function(e)
  {
    return(list())
  }
  
  agemixing.lme.fitter <- function(data = dplyr::filter(agemix.model[[1]], Gender =="male")){
    men.lme <- lme(pagerelform ~ agerelform0,
                   data = data,
                   control=lmeControl(maxIter=10000, returnObject=TRUE, opt = "optim"),
                   random = ~1 | ID,
                   method = "REML",
                   weight = varPower(value = 0.5, form = ~agerelform0 + 1))
  }
  
  
  scenario <- function(interventionlist, tasp.indicator) {
    switch(tasp.indicator+1, interventionlist[1:4], interventionlist[1:5])
  } 
  
  
  
  cd4.atARTinit <- function(datalist = datalist,
                            agegroup = c(15, 30),
                            timewindow = c(15, 30),
                            cd4count=350, site="All"){
    
    cd4.atARTinit <- age.group.time.window(datalist = datalist,
                                           agegroup = agegroup,
                                           timewindow = timewindow, site="All")
    
    cd4.atARTinit <- subset(cd4.atARTinit, TreatTime !=Inf) #HIV positive individuals
    
    raw.df <- data.frame(cd4.atARTinit)
    art.df <- subset(datalist$ttable, ID %in% cd4.atARTinit$ID &
                       TStart > timewindow[1] & TStart < timewindow[2])
    
    ##What if the person dropped out and come back again?
    art.df <- data.frame(dplyr::summarise(dplyr::group_by(art.df, ID, Gender),
                                          CD4atARTstart = min(CD4atARTstart)))
    
    #indicate those who started their treatment when their CD4 count was below a given threshold
    art.df <- art.df %>% dplyr::mutate(ART.start.CD4 = CD4atARTstart < cd4count)
    
    # Now we apply the left_join dplyr function to add the ART status to raw.df.
    raw.df <- dplyr::left_join(x = raw.df, y = art.df, by = c("ID", "Gender"))
    
    #provide a summary of those that are on treatment and those that started below a threshold
    cd4count.atARTInit <- data.frame(dplyr::summarise(dplyr::group_by(raw.df, Gender),
                                                      TotalCases = n(),
                                                      LessCD4initThreshold =sum(ART.start.CD4)))
    
    return(cd4count.atARTInit)
  }
  root.path <- dirname(getwd())
  destDir <- paste0(root.path, "/temp")
  age.distr <- agedistr.creator(shape = 5, scale = 65)
  cfg.list <- input.params.creator(population.eyecap.fraction = 0.21,#1,
                                   population.simtime = 40,
                                   population.nummen = 2500,
                                   population.numwomen = 2500,
                                   hivseed.time = 10,
                                   hivseed.type = "amount",
                                   hivseed.amount = 30,
                                   hivseed.age.min = 20,
                                   hivseed.age.max = 50,
                                   hivtransmission.param.a = -1,
                                   hivtransmission.param.b = -90,
                                   hivtransmission.param.c = 0.5,
                                   hivtransmission.param.f1 = log(2),
                                   hivtransmission.param.f2 = log(log(1.4) / log(2)) / 5,
                                   formation.hazard.agegapry.gap_factor_man_age = -0.01, #-0.01472653928518528523251061,
                                   formation.hazard.agegapry.gap_factor_woman_age = -0.01, #-0.0726539285185285232510561,
                                   formation.hazard.agegapry.meanage = -0.025,
                                   formation.hazard.agegapry.gap_factor_man_const = 0,
                                   formation.hazard.agegapry.gap_factor_woman_const = 0,
                                   formation.hazard.agegapry.gap_factor_man_exp = -1, #-6,#-1.5,
                                   formation.hazard.agegapry.gap_factor_woman_exp = -1, #-6,#-1.5,
                                   formation.hazard.agegapry.gap_agescale_man = 0.25,
                                   formation.hazard.agegapry.gap_agescale_woman = 0.25,#-0.30000007,#-0.03,
                                   debut.debutage = 15,
                                   conception.alpha_base = -2.5#,
                                   #person.art.accept.threshold.dist.fixed.value = 0
  )
  # cfg.list["diagnosis.baseline"] <- 100
  # cfg.list["diagnosis.HSV2factor"] <- 0
  # cfg.list["diagnosis.agefactor"] <- 0
  # cfg.list["diagnosis.beta"] <- 0
  # cfg.list["diagnosis.diagpartnersfactor"] <- 0
  # cfg.list["diagnosis.genderfactor"] <- 0
  # cfg.list["diagnosis.isdiagnosedfactor"] <- 0
  # cfg.list["diagnosis.t_max"] <- 200
  cfg.list["formation.hazard.agegapry.baseline"] <- 2
  cfg.list["mortality.aids.survtime.C"] <- 65
  cfg.list["mortality.aids.survtime.k"] <- -0.2
  cfg.list["monitoring.fraction.log_viralload"] <- 0.3
  cfg.list["dropout.interval.dist.uniform.min"] <- 100
  cfg.list["dropout.interval.dist.uniform.max"] <- 200
  
  cfg.list["person.agegap.man.dist.type"] <- "normal" #fixed
  #cfg.list["person.agegap.man.dist.fixed.value"] <- -6
  cfg.list["person.agegap.woman.dist.type"] <- "normal" #"fixed"
  #cfg.list["person.agegap.woman.dist.fixed.value"] <- -6
  
  cfg.list["mortality.aids.survtime.C"] <- 65
  cfg.list["mortality.aids.survtime.k"] <- -0.2
  #cfg.list["monitoring.cd4.threshold"] <- 0
  cfg.list["person.agegap.man.dist.normal.mu"] <- 0
  cfg.list["person.agegap.woman.dist.normal.mu"] <- 0
  cfg.list["person.agegap.man.dist.normal.sigma"] <- inputvector[2] ######### 3
  cfg.list["person.agegap.woman.dist.normal.sigma"] <- inputvector[2] ######### 3
  
  cfg.list["person.survtime.logoffset.dist.type"] <- "normal"
  cfg.list["person.survtime.logoffset.dist.normal.mu"] <- 0
  cfg.list["person.survtime.logoffset.dist.normal.sigma"] <- 0.1
  
  cfg <- cfg.list
  seedid <- inputvector[1]
  #cfg["person.agegap.man.dist.fixed.value"] <- -2 # inputvector[2]
  #cfg["person.agegap.woman.dist.fixed.value"] <- -2 # inputvector[2]
  cfg["formation.hazard.agegapry.gap_factor_man_exp"] <- inputvector[3] ######### -0.5
  cfg["formation.hazard.agegapry.gap_factor_woman_exp"] <- inputvector[3] ######### -0.5
  
  # Let's introduce ART, and evaluate whether the HIV prevalence drops less  rapidly
  art.intro <- list()
  art.intro["time"] <- 25
  art.intro["person.art.accept.threshold.dist.fixed.value"] <- inputvector[4] ######### 0.5
  art.intro["diagnosis.baseline"] <- 0#100
  art.intro["monitoring.cd4.threshold"] <- 100 # 1200
  #art.intro["monitoring.interval.piecewise.cd4s"] <- "0,1300"
  
  
  # Gradual increase in CD4 threshold. in 2007:200. in 2010:350. in 2013:500
  
  art.intro2 <- list()
  art.intro2["time"] <- 25 + inputvector[5] ######### 30
  art.intro2["monitoring.cd4.threshold"] <- 200
  
  art.intro3 <- list()
  art.intro3["time"] <- inputvector[4] + inputvector[5] + inputvector[6] ########### 33
  art.intro3["monitoring.cd4.threshold"] <- 350
  
  art.intro4 <- list()
  art.intro4["time"] <- inputvector[4] + inputvector[5] + inputvector[6] + inputvector[7] ########### 36
  art.intro4["monitoring.cd4.threshold"] <- 500
  
  art.intro5 <- list()
  art.intro5["time"] <- 38
  art.intro5["monitoring.cd4.threshold"] <- 5000 # This is equivalent to immediate access
  art.intro5["person.art.accept.threshold.dist.fixed.value"] <- inputvector[8] ########### 0.75
  
  tasp.indicator <- inputvector[9] # 1 if the scenario is TasP, 0 if the scenario is current status
  
  interventionlist <- list(art.intro, art.intro2, art.intro3, art.intro4, art.intro5)
  
  intervention <- scenario(interventionlist, tasp.indicator)
  
  results <- simpact.run(configParams = cfg,
                         destDir = destDir,
                         agedist = age.distr,
                         seed = seedid, #, Introducing ART has helped to keep the prevalence high
                         intervention = intervention)
  
  datalist.agemix <- readthedata(results)
  agemix.df <- agemix.df.maker(datalist.agemix)
  
  agemix.model <- pattern.modeller(dataframe = agemix.df,
                                   agegroup = c(15, 50),
                                   timepoint = datalist.agemix$itable$population.simtime[1],
                                   timewindow = 3)
  
  men.lme <- tryCatch(agemixing.lme.fitter(data = dplyr::filter(agemix.model[[1]], Gender =="male")),
                      error = agemixing.lme.errFunction) # Returns an empty list if the lme model can't be fitted
  
  bignumber <- NA # let's try if NA works (instead of 9999 for example)
  
  AAD <- ifelse(length(men.lme) > 0, mean(dplyr::filter(agemix.model[[1]], Gender =="male")$AgeGap), bignumber)
  SDAD <- ifelse(length(men.lme) > 0, sd(dplyr::filter(agemix.model[[1]], Gender =="male")$AgeGap), bignumber)
  powerm <- ifelse(length(men.lme) > 0, as.numeric(attributes(men.lme$apVar)$Pars["varStruct.power"]), bignumber)
  slopem <- ifelse(length(men.lme) > 0, summary(men.lme)$tTable[2, 1], bignumber)
  WVAD.base <- ifelse(length(men.lme) > 0, men.lme$sigma^2, bignumber)
  BVAD <- ifelse(length(men.lme) > 0, getVarCov(men.lme)[1,1], bignumber)
  
  #agegap.mean <- mean(datalist.agemix$rtable$AgeGap)
  #agegap.sd <- sd(datalist.agemix$rtable$AgeGap)
  hivprev.15.50 <- prevalence.calculator(datalist = datalist.agemix,
                                         agegroup = c(15, 50),
                                         timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[3]
  # ART coverage vector
  ART.cov.eval.timepoints <- seq(from = intervention[[1]]$time,
                                 to = datalist.agemix$itable$population.simtime[1])
  ART.cov.vector <- rep(NA, length(ART.cov.eval.timepoints))
  for (art.cov.index in 1:length(ART.cov.vector)){
    ART.cov.vector[art.cov.index] <- sum(ART.coverage.calculator(datalist = datalist.agemix,
                                                                 agegroup = c(15, 50),
                                                                 timepoint = ART.cov.eval.timepoints[art.cov.index])$sum.onART) /
      sum(ART.coverage.calculator(datalist = datalist.agemix,
                                  agegroup = c(15, 50),
                                  timepoint = ART.cov.eval.timepoints[art.cov.index])$sum.cases)
  }
  # Vector of the fraction of people who started their treatment when their CD4count was between specified values
  cd4.atARTinit.fractions.timepoints <- seq(from = intervention[[1]]$time + 5,
                                            to = datalist.agemix$itable$population.simtime[1],
                                            by = 5) #30, 35, 40
  cd4.any.vector <- cd4.lt100.vector <- cd4.100.200.vector <- cd4.200.350.vector <- cd4.350.500.vector <- cd4.500plus.vector <- rep(NA, length(cd4.atARTinit.fractions.timepoints))
  for (cd4.index in 1:length(cd4.lt100.vector)){
    cd4.lt100.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
                                                 TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
                                                 TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
                                                 CD4atARTstart < 100) %>% select(ID) %>% unique() %>% nrow()
    cd4.100.200.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
                                                   TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
                                                   TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
                                                   CD4atARTstart >= 100,
                                                   CD4atARTstart < 200) %>% select(ID) %>% unique() %>% nrow()
    cd4.200.350.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
                                                   TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
                                                   TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
                                                   CD4atARTstart >= 200,
                                                   CD4atARTstart < 350) %>% select(ID) %>% unique() %>% nrow()
    cd4.350.500.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
                                                   TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
                                                   TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
                                                   CD4atARTstart >= 350,
                                                   CD4atARTstart < 500) %>% select(ID) %>% unique() %>% nrow()
    cd4.500plus.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
                                                   TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
                                                   TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
                                                   CD4atARTstart >= 500) %>% select(ID) %>% unique() %>% nrow()
    cd4.any.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
                                               TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
                                               TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5)) %>% select(ID) %>% unique() %>% nrow()
  }
  
  incid.final <- incidence.calculator(datalist = datalist.agemix,
                                      agegroup = c(15, 50),
                                      timewindow = c((datalist.agemix$itable$population.simtime[1] - 2), datalist.agemix$itable$population.simtime[1]),
                                      only.active = "No")$incidence[3]
  
  growthrate <- pop.growth.calculator(datalist = datalist.agemix,
                                      timewindow = c(0, datalist.agemix$itable$population.simtime[1]))
  
  outputvector <- c(AAD, SDAD, powerm, slopem, WVAD.base, BVAD, hivprev.15.50, growthrate,
                    ART.cov.vector,
                    cd4.lt100.vector/cd4.any.vector,
                    cd4.100.200.vector/cd4.any.vector,
                    cd4.200.350.vector/cd4.any.vector,
                    cd4.350.500.vector/cd4.any.vector,
                    cd4.500plus.vector/cd4.any.vector,
                    incid.final)
  return(outputvector)
}






simpact.wrapper <- function(inputvector = input.vector){ # This function does not produce the incidence and does not have an input for the model scenario
  library(RSimpactHelper)
  library(RSimpactCyan)
  library(magrittr)
  library(dplyr)
  library(nlme)
  library(lme4)
  library(fitdistrplus)
  library(lmtest)
  library(tidyr)
  library(data.table)
  
  agemixing.lme.errFunction <- function(e)
  {
    return(list())
  }
  
  simpact.errFunction <-function(e){
    if (length(grep("NaN",e$message)) != 0){
      return(list())
    }
  }
  
  # agemixing.lme.fitter <- function(data = dplyr::filter(agemix.model[[1]], Gender =="male")){
  #   men.lme <- lme(pagerelform ~ agerelform0,
  #                  data = data,
  #                  control=lmeControl(maxIter=10000, returnObject=TRUE, opt = "optim"),
  #                  random = ~1 | ID,
  #                  method = "REML",
  #                  weight = varPower(value = 0.5, form = ~agerelform0 + 1))
  # }
  
  ampmodel <- function(data = dplyr::filter(agemix.model[[1]], Gender =="male")) {
    lmer(pagerelform ~ agerelform0 + (1 | ID),
         data = data,
         REML = TRUE)  
  }
  
  
  
  bvar <- function(model) {
    
    # Outputs a df with between-subject variance, upr & lwr limits
    
    # Must take an merMod  object
    
    bsd <- as.numeric(as.data.frame(VarCorr(model))[1,5])
    
    
  }
  
  
  
  degree.df.maker <- function (dataframe.df, agegroup = c(15, 30), hivstatus = 0, 
                               survey.time = 40, window.width = 1, gender.degree = "female", 
                               only.new = TRUE) 
  {
    dataframe.rels.df <- dataframe.df
    dataframe.rels.df <- dplyr::select(dataframe.rels.df, -episodeorder, -FormTime, -DisTime)
    dataframe.rels.df <- unique.data.frame(dataframe.rels.df)
    rels.form.dis.df <- dplyr::summarise(dplyr::group_by(dataframe.df, 
                                                         relid), FormTime = min(FormTime), DisTime = max(DisTime))
    dfnew <- dplyr::left_join(x = dataframe.rels.df, y = rels.form.dis.df, 
                              by = "relid")
    dfnew <- dplyr::filter(dfnew, TOD > survey.time)
    {
      if (hivstatus == 0) {
        dfnew <- dplyr::filter(dfnew, InfectTime > survey.time)
      }
      else if (hivstatus == 1) {
        dfnew <- dplyr::filter(dfnew, InfectTime <= survey.time)
      }
    }
    {
      if (only.new) {
        dfnew <- dplyr::filter(dfnew, FormTime >= survey.time - 
                                 window.width, FormTime < survey.time, DisTime > 
                                 survey.time - window.width, Gender == gender.degree, 
                               survey.time - TOB >= agegroup[1], survey.time - 
                                 TOB < agegroup[2])
      }
      else {
        dfnew <- dplyr::filter(dfnew, FormTime < survey.time, 
                               DisTime > survey.time - window.width, Gender == 
                                 gender.degree, survey.time - TOB >= agegroup[1], 
                               survey.time - TOB < agegroup[2])
      }
    }
    uniqueOut <- dfnew %>% dplyr::select(ID, relid) %>% distinct %>% 
      rename(Degree = relid)
    if (dim(uniqueOut)[1] != 0) {
      degreedata.df <- aggregate(Degree ~ ID, data = uniqueOut, 
                                 length)
    } else {
      degreedata.df <- data.frame(ID = NA, Degree = NA)
    }
    return(degreedata.df)
  }
  
  # scenario <- function(interventionlist, tasp.indicator) {
  #   switch(tasp.indicator+1, interventionlist[1:4], interventionlist[1:5])
  # } 
  
  
  
  
  
  concurr.pointprev.calculator <- function(datalist,
                                           timepoint = datalist$itable$population.simtime[1] - 0.5){ #DTP = datalist$ptable, DTE = datalist$etable, cfg = configfile){
    #DTP <- datalist$ptable
    #DTL <- datalist$ltable
    output <- data.table()
    DTalive.infected <- alive.infected(datalist = datalist,
                                       timepoint = timepoint, site = "All") # First we only take the data of people who were alive at time_i
    agemix.df <- agemix.df.maker(datalist)
    degrees.df <- degree.df.maker(dataframe.df = agemix.df,
                                  agegroup = c(15, 50),
                                  hivstatus = 2,
                                  survey.time = timepoint,
                                  window.width = 0,
                                  gender.degree = "male",
                                  only.new = FALSE)
    
    number.people.with.cps <- sum(degrees.df$Degree > 1)
    popsize <- nrow(DTalive.infected)
    concurr.pointprevalence <- number.people.with.cps / popsize
    #output <- rbind(output, concurrdata)
    #outputlist <- list(output=output)
    #return(outputlist)
    return(concurr.pointprevalence)
  }
  
  
  
  
  cd4.atARTinit <- function(datalist = datalist,
                            agegroup = c(15, 30),
                            timewindow = c(15, 30),
                            cd4count=350, site="All"){
    
    cd4.atARTinit <- age.group.time.window(datalist = datalist,
                                           agegroup = agegroup,
                                           timewindow = timewindow, site="All")
    
    cd4.atARTinit <- subset(cd4.atARTinit, TreatTime !=Inf) #HIV positive individuals
    
    raw.df <- data.frame(cd4.atARTinit)
    art.df <- subset(datalist$ttable, ID %in% cd4.atARTinit$ID &
                       TStart > timewindow[1] & TStart < timewindow[2])
    
    ##What if the person dropped out and come back again?
    art.df <- data.frame(dplyr::summarise(dplyr::group_by(art.df, ID, Gender),
                                          CD4atARTstart = min(CD4atARTstart)))
    
    #indicate those who started their treatment when their CD4 count was below a given threshold
    art.df <- art.df %>% dplyr::mutate(ART.start.CD4 = CD4atARTstart < cd4count)
    
    # Now we apply the left_join dplyr function to add the ART status to raw.df.
    raw.df <- dplyr::left_join(x = raw.df, y = art.df, by = c("ID", "Gender"))
    
    #provide a summary of those that are on treatment and those that started below a threshold
    cd4count.atARTInit <- data.frame(dplyr::summarise(dplyr::group_by(raw.df, Gender),
                                                      TotalCases = n(),
                                                      LessCD4initThreshold =sum(ART.start.CD4)))
    
    return(cd4count.atARTInit)
  }
  root.path <- dirname(getwd())
  destDir <- paste0(root.path, "/temp")
  age.distr <- agedistr.creator(shape = 5, scale = 65)
  cfg.list <- input.params.creator(population.eyecap.fraction = 0.2, #0.21,#1,
                                   population.simtime = 35, #40,
                                   population.nummen = 2500,
                                   population.numwomen = 2500,
                                   hivseed.time = 10,
                                   hivseed.type = "amount",
                                   hivseed.amount = 25, #30,
                                   hivseed.age.min = 20,
                                   hivseed.age.max = 50,
                                   hivtransmission.param.a = -1,
                                   hivtransmission.param.b = -90,
                                   hivtransmission.param.c = 0.5,
                                   hivtransmission.param.f1 = log(inputvector[2]) , #log(2),
                                   hivtransmission.param.f2 = log(log(sqrt(inputvector[2])) / log(inputvector[2])) / 5, #log(log(1.4) / log(2)) / 5,
                                   formation.hazard.agegapry.gap_factor_man_age = -0.01, #-0.01472653928518528523251061,
                                   formation.hazard.agegapry.gap_factor_woman_age = -0.01, #-0.0726539285185285232510561,
                                   formation.hazard.agegapry.meanage = -0.025,
                                   formation.hazard.agegapry.gap_factor_man_const = 0,
                                   formation.hazard.agegapry.gap_factor_woman_const = 0,
                                   formation.hazard.agegapry.gap_factor_man_exp = -1, #-6,#-1.5,
                                   formation.hazard.agegapry.gap_factor_woman_exp = -1, #-6,#-1.5,
                                   formation.hazard.agegapry.gap_agescale_man = inputvector[3], # 0.25,
                                   formation.hazard.agegapry.gap_agescale_woman = inputvector[3], # 0.25,#-0.30000007,#-0.03,
                                   debut.debutage = 15,
                                   conception.alpha_base = inputvector[14]#-2.5#,
                                   #person.art.accept.threshold.dist.fixed.value = 0
  )
  
  # cfg.list["diagnosis.baseline"] <- 100
  # cfg.list["diagnosis.HSV2factor"] <- 0
  # cfg.list["diagnosis.agefactor"] <- 0
  # cfg.list["diagnosis.beta"] <- 0
  # cfg.list["diagnosis.diagpartnersfactor"] <- 0
  # cfg.list["diagnosis.genderfactor"] <- 0
  # cfg.list["diagnosis.isdiagnosedfactor"] <- 0
  # cfg.list["diagnosis.t_max"] <- 200
  cfg.list["formation.hazard.agegapry.baseline"] <- 2
  cfg.list["mortality.aids.survtime.C"] <- 65
  cfg.list["mortality.aids.survtime.k"] <- -0.2
  cfg.list["monitoring.fraction.log_viralload"] <- 0.3
  cfg.list["dropout.interval.dist.uniform.min"] <- 100
  cfg.list["dropout.interval.dist.uniform.max"] <- 200
  
  
  cfg.list["person.agegap.man.dist.type"] <- "normal" #fixed
  #cfg.list["person.agegap.man.dist.fixed.value"] <- -6
  cfg.list["person.agegap.woman.dist.type"] <- "normal" #"fixed"
  #cfg.list["person.agegap.woman.dist.fixed.value"] <- -6
  
  cfg.list["mortality.aids.survtime.C"] <- 65
  cfg.list["mortality.aids.survtime.k"] <- -0.2
  cfg.list["monitoring.cd4.threshold"] <- 0
  cfg.list["person.agegap.man.dist.normal.mu"] <- inputvector[4] # 0
  cfg.list["person.agegap.woman.dist.normal.mu"] <- inputvector[4] # 0
  cfg.list["person.agegap.man.dist.normal.sigma"] <- inputvector[5] ######### 3
  cfg.list["person.agegap.woman.dist.normal.sigma"] <- inputvector[5] ######### 3
  cfg.list["person.eagerness.man.dist.gamma.a"] <- inputvector[6] ######### 0.23
  cfg.list["person.eagerness.woman.dist.gamma.a"] <- inputvector[7] ######### 0.23
  cfg.list["person.eagerness.man.dist.gamma.b"] <- inputvector[8] ######### 45
  cfg.list["person.eagerness.woman.dist.gamma.b"] <- inputvector[9] ######### 45
  
  
  cfg.list["person.survtime.logoffset.dist.type"] <- "normal"
  cfg.list["person.survtime.logoffset.dist.normal.mu"] <- 0
  cfg.list["person.survtime.logoffset.dist.normal.sigma"] <- 0.1
  
  cfg <- cfg.list
  
  cfg["population.maxevents"] <- as.numeric(cfg.list["population.simtime"][1]) * as.numeric(cfg.list["population.nummen"][1]) * 3
  cfg["monitoring.fraction.log_viralload"] <- 0.3
  cfg["person.vsp.toacute.x"] <- 5 # See Bellan PLoS Medicine
  
  seedid <- inputvector[1]
  #cfg["person.agegap.man.dist.fixed.value"] <- -2 # inputvector[2]
  #cfg["person.agegap.woman.dist.fixed.value"] <- -2 # inputvector[2]
  cfg["formation.hazard.agegapry.gap_factor_man_exp"] <- inputvector[10] ######### -0.5
  cfg["formation.hazard.agegapry.gap_factor_woman_exp"] <- inputvector[10] ######### -0.5
  cfg["formation.hazard.agegapry.baseline"] <- inputvector[11]
  
  cfg["formation.hazard.agegapry.numrel_man"] <- inputvector[12]
  cfg["formation.hazard.agegapry.numrel_woman"] <- inputvector[13]
  # inputvector[14] is conception.alpha.base (higher up)
  cfg["dissolution.alpha_0"] <- inputvector[15]
  cfg["dissolution.alpha_4"] <- inputvector[16]
  
  # Let's introduce ART, and evaluate whether the HIV prevalence drops less  rapidly
  art.intro <- list()
  art.intro["time"] <- 25
  art.intro["person.art.accept.threshold.dist.fixed.value"] <- 0.5 # inputvector[4] ######### 0.5
  art.intro["diagnosis.baseline"] <- 0#100
  art.intro["monitoring.cd4.threshold"] <- 100 # 1200
  #art.intro["monitoring.interval.piecewise.cd4s"] <- "0,1300"
  
  
  # Gradual increase in CD4 threshold. in 2007:200. in 2010:350. in 2013:500
  
  art.intro2 <- list()
  art.intro2["time"] <- 25 + 5 # inputvector[5] ######### 30
  art.intro2["monitoring.cd4.threshold"] <- 200
  
  art.intro3 <- list()
  art.intro3["time"] <- 33 # inputvector[4] + inputvector[5] + inputvector[6] ########### 33
  art.intro3["monitoring.cd4.threshold"] <- 350
  
  art.intro4 <- list()
  art.intro4["time"] <- 3 # inputvector[4] + inputvector[5] + inputvector[6] + inputvector[7] ########### 36
  art.intro4["monitoring.cd4.threshold"] <- 500
  
  art.intro5 <- list()
  art.intro5["time"] <- 38
  art.intro5["monitoring.cd4.threshold"] <- 5000 # This is equivalent to immediate access
  art.intro5["person.art.accept.threshold.dist.fixed.value"] <- 0.5 # inputvector[8] ########### 0.75
  
  # tasp.indicator <- inputvector[9] # 1 if the scenario is TasP, 0 if the scenario is current status
  
  interventionlist <- list(art.intro, art.intro2, art.intro3, art.intro4, art.intro5)
  
  intervention <- interventionlist # scenario(interventionlist, tasp.indicator)
  
  results <- tryCatch(simpact.run(configParams = cfg,
                         destDir = destDir,
                         agedist = age.distr,
                         seed = seedid, #, Introducing ART has helped to keep the prevalence high
                         intervention = intervention),
                      error = simpact.errFunction)
  # results <- simpact.run(configParams = cfg,
  #                        destDir = destDir,
  #                        agedist = age.distr,
  #                        seed = seedid, #, Introducing ART has helped to keep the prevalence high
  #                        intervention = intervention)
  if (length(results) == 0){
    outputvector <- rep(NA, 17)
  } else {
    if (as.numeric(results["eventsexecuted"]) >= (as.numeric(cfg["population.maxevents"]) - 1)) {
      outputvector <- rep(NA, 17)
    } else {
    datalist.agemix <- readthedata(results)
    agemix.df <- agemix.df.maker(datalist.agemix)
    
    agemix.model <- pattern.modeller(dataframe = agemix.df,
                                     agegroup = c(15, 50),
                                     timepoint = datalist.agemix$itable$population.simtime[1],
                                     timewindow = 1)#3)
    
    # men.lme <- tryCatch(agemixing.lme.fitter(data = dplyr::filter(agemix.model[[1]], Gender =="male")),
    #                     error = agemixing.lme.errFunction) # Returns an empty list if the lme model can't be fitted
    
    men.lmer <- tryCatch(ampmodel(data = dplyr::filter(agemix.model[[1]], Gender =="male")),
                         error = agemixing.lme.errFunction) # Returns an empty list if the lme model can't be fitted
    
    bignumber <- NA # let's try if NA works (instead of 9999 for example)
    
    AAD.male <- ifelse(length(men.lmer) > 0, mean(dplyr::filter(agemix.model[[1]], Gender =="male")$AgeGap), bignumber)
    SDAD.male <- ifelse(length(men.lmer) > 0, sd(dplyr::filter(agemix.model[[1]], Gender =="male")$AgeGap), bignumber)
    #powerm <- ifelse(length(men.lme) > 0, as.numeric(attributes(men.lme$apVar)$Pars["varStruct.power"]), bignumber)
    slope.male <- ifelse(length(men.lmer) > 0, summary(men.lmer)$coefficients[2, 1], bignumber) #summary(men.lmer)$tTable[2, 1], bignumber)
    WSD.male <- ifelse(length(men.lmer) > 0, summary(men.lmer)$sigma, bignumber) #WVAD.base <- ifelse(length(men.lme) > 0, men.lme$sigma^2, bignumber)
    
    BSD.male <- ifelse(length(men.lmer) > 0, bvar(men.lmer), bignumber) # Bad name for the function because it actually extracts between subject standard deviation # BVAD <- ifelse(length(men.lmer) > 0, getVarCov(men.lme)[1,1], bignumber)
    
    intercept.male <- ifelse(length(men.lmer) > 0, summary(men.lmer)$coefficients[1,1] - 15, bignumber) 
    
    #agegap.mean <- mean(datalist.agemix$rtable$AgeGap)
    #agegap.sd <- sd(datalist.agemix$rtable$AgeGap)
    
    
    ###
    # Now we fit the negative binomial distribution
    ###
    degrees.df <- degree.df.maker(dataframe.df = agemix.df,
                                  agegroup = c(18, 50),
                                  hivstatus = 2,
                                  survey.time = datalist.agemix$itable$population.simtime[1],
                                  window.width = 1,
                                  gender.degree = "male",
                                  only.new = TRUE)
    
    
    # If we want to know % of men who had 0 partners in the past 12 months,
    # We need to compare nrow(degree.df) with the number of 18-50 year old men #HIV negative women
    # that were alive at the time of the survey
    allsurveymen <- dplyr::filter(datalist.agemix$ptable,
                                  Gender == 1, # Male
                                  TOD > datalist.agemix$itable$population.simtime[1], # Still alive at the time of the survey
                                  TOB <= datalist.agemix$itable$population.simtime[1] - 18, # Not younger than 18 at the time of the survey
                                  TOB > datalist.agemix$itable$population.simtime[1] - 50)#, # Not older than 50 at the time of the survey
    #InfectTime > datalist.agemix$itable$population.simtime[1]) # HIV negative at the time of the survey
    
    # Creating the vector of degrees
    degree.vector <- c(rep(0, times = (nrow(allsurveymen) - nrow(degrees.df))), degrees.df$Degree)
    meandegree.male <- mean(degree.vector)
    # hist(degree.vector, 10)
    # degree.vector <- rnbinom(n = 100, size =1.28, mu = 0.66) # PLACEHOLDER FOR NOW
    # Fitting the negative binomial distribution to this vector
    
    fit.negbin <- tryCatch(fitdist(degree.vector, "nbinom"), error = agemixing.lme.errFunction)
    shape.nb.male <- ifelse(length(fit.negbin) > 0, as.numeric(fit.negbin$estimate[2]), bignumber)
    scale.nb.male <- ifelse(length(fit.negbin) > 0, as.numeric(fit.negbin$estimate[1]), bignumber) #(theta = p/(1-p))
    
    #   degrees.df <- data.frame(degree = degree.vector)
    #   # Model for black men in the last year
    #   nb.fit <- glm.nb(degree~1,
    #                        data = degrees.df,
    #                        control = glm.control(maxit = 100000, trace = 3),
    #                        init.theta = 1)
    # summary(nb.fit) # intercept exp(0.25), theta = 0.65
    # shape.nb <- exp(as.numeric(nb.fit$coefficients)) #(r)
    # scale.nb <- as.numeric(nb.fit$theta) #(theta = p/(1-p))
    
    
    # Concurrency point prevalence 6 months before a survey, among men
    pp.cp.6months.male <- concurr.pointprev.calculator(datalist = datalist.agemix,
                                                       timepoint = datalist$itable$population.simtime[1] - 0.5)
    
    
    hiv.prev.lt25.women <- prevalence.calculator(datalist = datalist.agemix,
                                                 agegroup = c(15, 25),
                                                 timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[2]
    hiv.prev.lt25.men <- prevalence.calculator(datalist = datalist.agemix,
                                               agegroup = c(15, 25),
                                               timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[1]
    hiv.prev.25.34.women <- prevalence.calculator(datalist = datalist.agemix,
                                                  agegroup = c(25, 35),
                                                  timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[2]
    hiv.prev.25.34.men <- prevalence.calculator(datalist = datalist.agemix,
                                                agegroup = c(25, 35),
                                                timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[1]
    hiv.prev.35.44.women <- prevalence.calculator(datalist = datalist.agemix,
                                                  agegroup = c(35, 45),
                                                  timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[2]
    hiv.prev.35.44.men <- prevalence.calculator(datalist = datalist.agemix,
                                                agegroup = c(35, 45),
                                                timepoint = datalist.agemix$itable$population.simtime[1])$pointprevalence[1]
    
    
    # ART coverage vector
    # ART.cov.eval.timepoints <- seq(from = intervention[[1]]$time,
    #                                to = datalist.agemix$itable$population.simtime[1])
    # ART.cov.vector <- rep(NA, length(ART.cov.eval.timepoints))
    # for (art.cov.index in 1:length(ART.cov.vector)){
    #   ART.cov.vector[art.cov.index] <- sum(ART.coverage.calculator(datalist = datalist.agemix,
    #                                                                agegroup = c(15, 50),
    #                                                                timepoint = ART.cov.eval.timepoints[art.cov.index])$sum.onART) /
    #     sum(ART.coverage.calculator(datalist = datalist.agemix,
    #                                 agegroup = c(15, 50),
    #                                 timepoint = ART.cov.eval.timepoints[art.cov.index])$sum.cases)
  # }
  # Vector of the fraction of people who started their treatment when their CD4count was between specified values
  # cd4.atARTinit.fractions.timepoints <- seq(from = intervention[[1]]$time + 5,
  #                                         to = datalist.agemix$itable$population.simtime[1],
  #                                         by = 5) #30, 35, 40
  # cd4.any.vector <- cd4.lt100.vector <- cd4.100.200.vector <- cd4.200.350.vector <- cd4.350.500.vector <- cd4.500plus.vector <- rep(NA, length(cd4.atARTinit.fractions.timepoints))
  # for (cd4.index in 1:length(cd4.lt100.vector)){
  #   cd4.lt100.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
  #                                                      TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
  #                                                      TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
  #                                                      CD4atARTstart < 100) %>% select(ID) %>% unique() %>% nrow()
  #   cd4.100.200.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
  #                                                      TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
  #                                                      TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
  #                                                      CD4atARTstart >= 100,
  #                                                      CD4atARTstart < 200) %>% select(ID) %>% unique() %>% nrow()
  #   cd4.200.350.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
  #                                                      TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
  #                                                      TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
  #                                                      CD4atARTstart >= 200,
  #                                                      CD4atARTstart < 350) %>% select(ID) %>% unique() %>% nrow()
  #   cd4.350.500.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
  #                                                      TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
  #                                                      TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
  #                                                      CD4atARTstart >= 350,
  #                                                      CD4atARTstart < 500) %>% select(ID) %>% unique() %>% nrow()
  #   cd4.500plus.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
  #                                                      TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
  #                                                      TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5),
  #                                                      CD4atARTstart >= 500) %>% select(ID) %>% unique() %>% nrow()
  #   cd4.any.vector[cd4.index] <- dplyr::filter(datalist.agemix$ttable,
  #                                                      TStart < cd4.atARTinit.fractions.timepoints[cd4.index],
  #                                                      TStart >= (cd4.atARTinit.fractions.timepoints[cd4.index] - 5)) %>% select(ID) %>% unique() %>% nrow()
  # }
  
  # incid.final <- incidence.calculator(datalist = datalist.agemix,
  #                                     agegroup = c(15, 50),
  #                                     timewindow = c((datalist.agemix$itable$population.simtime[1] - 2), datalist.agemix$itable$population.simtime[1]),
  #                                     only.active = "No")$incidence[3]
  
  growthrate <- pop.growth.calculator(datalist = datalist.agemix,
                                      timewindow = c(0, datalist.agemix$itable$population.simtime[1]))
  
  outputvector <- c(AAD.male, SDAD.male, slope.male, WSD.male, BSD.male, intercept.male,
                    shape.nb.male, scale.nb.male,
                    meandegree.male,
                    pp.cp.6months.male,
                    hiv.prev.lt25.women,
                    hiv.prev.lt25.men,
                    hiv.prev.25.34.women,
                    hiv.prev.25.34.men,
                    hiv.prev.35.44.women,
                    hiv.prev.35.44.men, 
                    exp(growthrate))
    }
  }
  return(outputvector)
}

```

#### Input parameters
1. hivtransmission.param.f1 (2)
2. formation.hazard.agegapry.gap_agescale_man = formation.hazard.agegapry.gap_agescale_woman (0.25)
3. person.agegap.man.dist.normal.mu = person.agegap.woman.dist.normal.mu (0)
4. person.agegap.man.dist.normal.sigma = person.agegap.woman.dist.normal.sigma (3)
5. person.person.eagerness.man.dist.gamma.a (0.23)
6. person.person.eagerness.woman.dist.gamma.a (0.23)
7. person.person.eagerness.man.dist.gamma.b (45)
8. person.person.eagerness.woman.dist.gamma.b (45)
9. formation.hazard.agegapry.gap_factor_man_exp = formation.hazard.agegapry.gap_factor_woman_exp (-0.5)
10. formation.hazard.agegapry.baseline (2)
11. formation.hazard.agegapry.numrel_man (-0.5)
12. formation.hazard.agegapry.numrel_woman (-0.5)
13. conception.alpha_base (-2.5)
14. dissolution.alpha_0 (-0.52)
15. dissolution.alpha_4 (-0.05)
  
  
#### Output statistics (and targets)

1. AAD.male (4)
2. SDAD.male (4)
3. slope.male (0.7)
4. WSD.male (3)
5. BSD.male (1.5)
6. intercept.male (-1)
7. shape.nb.male (1.29)
8. scale.nb.male (0.66)
9. meandegree.male (1)
10. pp.cp.6months.male (0.134)
11. hiv.prev.lt25.women (0.2)
12. hiv.prev.lt25.men (0.1)
13. hiv.prev.25.34.women (0.42)
14. hiv.prev.25.34.men (0.17)
15. hiv.prev.35.44.women (0.37)
16. hiv.prev.35.44.men (0.24)
17. exp(growthrate)) (1.01)
  
  
  
  
  
  

```{r define.parallel.function.evaluator, echo = FALSE}
# A function to run Simpact in parallel
simpact.parallel <- function(model = simpact.wrapper,
                             actual.input.matrix = matrix(rep(c(1:15), 16), nrow = 16),
                             #nb_simul = 16,
                             seed_count = 0,
                             n_cluster = 8){
  cl <- makeCluster(getOption("cl.cores", n_cluster))
  tab_simul_summarystat = NULL
  list_param <- list(NULL)
  tab_param <- NULL
  paramtemp <- NULL
  simultemp <- NULL

  nb_simul <- nrow(actual.input.matrix)

  for (i in 1:nb_simul) {
    l <- ncol(actual.input.matrix)
    param <- c((seed_count + i), actual.input.matrix[i, ])
    list_param[[i]] <- param
    tab_param <- rbind(tab_param, param[2:(l + 1)])
    paramtemp <- rbind(paramtemp, param[2:(l + 1)])
  }
  list_simul_summarystat = parLapplyLB(cl, list_param,
                                       model)
  tab_simul_summarystat <- do.call(rbind, list_simul_summarystat)
  stopCluster(cl)
  return(tab_simul_summarystat)
}

```



Let's create the "truth" with the master model.
```{r truth, cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE, results = "hide", eval = FALSE}
reps <- 2

target.vector.master <- c(1.1, 0.25, 0, 3, 0.23, 0.23, 45, 45, -0.5, 2.8, -0.2, -0.2, -2.5, -0.52, -0.05)
test.inputvectorplusseed <- c(1, target.vector.master)
# 1. hivtransmission.param.f1 (2)
# 2. formation.hazard.agegapry.gap_agescale_man = formation.hazard.agegapry.gap_agescale_woman (0.25)
# 3. person.agegap.man.dist.normal.mu = person.agegap.woman.dist.normal.mu (0)
# 4. person.agegap.man.dist.normal.sigma = person.agegap.woman.dist.normal.sigma (3)
# 5. person.person.eagerness.man.dist.gamma.a (0.23)
# 6. person.person.eagerness.woman.dist.gamma.a (0.23)
# 7. person.person.eagerness.man.dist.gamma.b (45)
# 8. person.person.eagerness.woman.dist.gamma.b (45)
# 9. formation.hazard.agegapry.gap_factor_man_exp = formation.hazard.agegapry.gap_factor_woman_exp (-0.5)
# 10. formation.hazard.agegapry.baseline (0)
# 11. formation.hazard.agegapry.numrel_man (-0.5)
# 12. formation.hazard.agegapry.numrel_woman (-0.5)
# 13. conception.alpha_base (-2.5)
# 14. dissolution.alpha_0 (-0.52)
# 15. dissolution.alpha_4 (-0.05))

simpact.wrapper(test.inputvectorplusseed)
# 1. AAD.male (4)
# 2. SDAD.male (4)
# 3. slope.male (0.7)
# 4. WSD.male (3)
# 5. BSD.male (1.5)
# 6. intercept.male (-1)
# 7. shape.nb.male (1.29)
# 8. scale.nb.male (0.66)
# 9. meandegree.male (1)
# 10. pp.cp.6months.male (0.134)
# 11. hiv.prev.lt25.women (0.2)
# 12. hiv.prev.lt25.men (0.1)
# 13. hiv.prev.25.34.women (0.42)
# 14. hiv.prev.25.34.men (0.17)
# 15. hiv.prev.35.44.women (0.37)
# 16. hiv.prev.35.44.men (0.24)
# 17. exp(growthrate)) (1.01)

targets.empirical <- c(4, 4, 0.7, 3, 1.5, -1, 1.29, 0.66, 1, 0.134, 0.2, 0.1, 0.42, 0.17, 0.37, 0.24, 1.01)
targets.master <- c(4.0651198,
                    3.5641622,
                    0.5463380,
                    1.8322277,
                    1.3357401,
                    -0.6137708,
                    0.4686528,
                    2.1738464,
                    0.4688209,
                    0.1203855,
                    0.3389044,
                    0.2751678,
                    0.3911846,
                    0.5899390,
                    0.3227513,
                    0.4395604,
                    1.0111390)
  
design.matrix.control <- matrix(rep(target.vector.master, reps), nrow = reps, byrow = TRUE)

design.matrix.interv <- matrix(rep(c(3, -0.5, 0.5, 5, 3, 3, 0.75, 1), reps), nrow = reps, byrow = TRUE)
test.mat <- matrix(data = NA, nrow = 6, ncol = 17)
for (test.i in 1:6){
  test.mat[test.i, ] <- simpact.wrapper(c(test.i, experiments[test.i, ]))
}

sumsmstats.control.df <- simpact.parallel(model = simpact.wrapper,
                                  actual.input.matrix = experiments,#design.matrix.control,
                                  seed_count = 0,
                                  n_cluster = 8)
sumsmstats.interv.df <- simpact.parallel(model = simpact.wrapper.master,
                                  actual.input.matrix = design.matrix.interv,
                                  seed_count = 0,
                                  n_cluster = 8)

```


```{r loadmastermodeloutput}
root.path <- dirname(getwd())
load(file = paste0(root.path, "/MiceABC/incidence.rel.reduc.RData"))
```



Now let's subtract the incidence estimates from one another.
```{r impact.estimation}

summary.interv <- summary(sumsmstats.interv.df)
#colMeans(sumsmstats.interv.df, na.rm = TRUE)

#lastcolumn <- ncol(sumsmstats.control.df)
#incidence.rel.reduc <- (sumsmstats.control.df[,lastcolumn] - sumsmstats.interv.df[,lastcolumn]) / sumsmstats.control.df[,lastcolumn]
#hist(incidence.rel.reduc, 20)
#summary(incidence.rel.reduc)
#predict.95.percent.interval.incidence.rel.reduc <- quantile(incidence.rel.reduc, probs = c(0.025, 0.975), na.rm = TRUE)

summary.interv.master <- summary.interv # summary(sumsmstats.interv.df)
target.vector.master <- colMeans(sumsmstats.interv.df, na.rm =TRUE)
target.vector.trainer <- head(target.vector.master, -1)
target.vector.trainer[9:length(target.vector.trainer)] <- exp(target.vector.trainer[9:length(target.vector.trainer)])
# We're turning target zeros into target ones
```


```{r myprob}
mice.impute.myprob <- function (y, ry, x, ...) 
{
    #aug <- mice:::augment(y, ry, x, ...)
    #x <- aug$x
    #y <- aug$y
    #ry <- aug$ry
    #w <- aug$w
    x <- cbind(1, as.matrix(x))
    expr <- expression(glm.fit(x[ry, ], y[ry], family = binomial(link = logit)))# expression(glm.fit(x[ry, ], y[ry], family = binomial(link = logit), weights = w[ry]))
    fit <- suppressWarnings(eval(expr))
    fit.sum <- summary.glm(fit)
    beta <- coef(fit)
    rv <- t(chol(mice:::sym(fit.sum$cov.unscaled)))
    beta.star <- beta + rv %*% rnorm(ncol(rv))
    p <- 1/(1 + exp(-(x[!ry, ] %*% beta.star)))
    # vec <- (runif(nrow(p)) <= p)
    # vec[vec] <- 1
    # if (is.factor(y)) {
    #     vec <- factor(vec, c(0, 1), levels(y))
    # }
    # return(vec)
    return(p)
}
```


```{r MICE_ABC, cache = TRUE, eval = FALSE}
ptm <- proc.time()

# 1. hivtransmission.param.f1 (2)
# 2. formation.hazard.agegapry.gap_agescale_man = formation.hazard.agegapry.gap_agescale_woman (0.25)
# 3. person.agegap.man.dist.normal.mu = person.agegap.woman.dist.normal.mu (0)
# 4. person.agegap.man.dist.normal.sigma = person.agegap.woman.dist.normal.sigma (3)
# 5. person.person.eagerness.man.dist.gamma.a (0.23)
# 6. person.person.eagerness.woman.dist.gamma.a (0.23)
# 7. person.person.eagerness.man.dist.gamma.b (45)
# 8. person.person.eagerness.woman.dist.gamma.b (45)
# 9. formation.hazard.agegapry.gap_factor_man_exp = formation.hazard.agegapry.gap_factor_woman_exp (-0.5)
# 10. formation.hazard.agegapry.baseline (0)
# 11. formation.hazard.agegapry.numrel_man (-0.5)
# 12. formation.hazard.agegapry.numrel_woman (-0.5)
# 13. conception.alpha_base (-2.5)
# 14. dissolution.alpha_0 (-0.52)
# 15. dissolution.alpha_4 (-0.05))

# inputs: c(1.1, 0.25, 0, 3, 0.23, 0.23, 45, 45, -0.5, 2.8, -0.2, -0.2, -2.5, -0.52, -0.05)

MICE_ABC_testoutput <- MICE_ABC(targets = targets.master, #targets.empirical, # 17 output statistics c(4, 4, 0.7, 3, 1.5, -1, 1.29, 0.66, 1, 0.134, 0.2, 0.1, 0.42, 0.17, 0.37, 0.24, 1.01)
                                 n.experiments = 128,
                                 lls = c(1,  0.12, -0.3, 2.5, 0.1, 0.1, 20, 20, -0.8, 2, -0.35, -0.35, -3.6, -0.8, -0.16), #c(2, -1,   0.1, 2, 1, 1, 0.3), #c(0.1, -3, 0.1,  0,  0,  0, 0.2),
                                 uls = c(1.2, 0.37, 0.3, 3.5, 0.4, 0.4, 66, 66, -0.25, 3.9, -0.1, -0.1, -1.4, -0.3,  -0.001), #c(4, -0.2, 0.6, 8, 6, 6, 0.95), #c(5, -0.1, 1.0, 10, 10, 10, 1.0),
                                 model = simpact.wrapper,
                                 maxit = 20,
                                 maxwaves = 2, # and we can also try 10 to do the same as the 10 waves of Lenormand
                                 #reps = 5,
                                 alpha = 0.25,
                                 saturation.crit = 0)
mice.timeused <- proc.time() - ptm
mice.timeused # xxxx seconds
```

```{r save.calibration.results, eval = FALSE}
root.path <- dirname(getwd())
save(MICE_ABC_testoutput, file = paste0(root.path, "/MiceABC/mice.age-mixing.RData"))

```
Now let's explore and visualise the results
```{r vis.calib.results}
root.path <- dirname(getwd())
load(file = paste0(root.path, "/MiceABC/reject.tasp.RData"))
load(file = paste0(root.path, "/MiceABC/mice.tasp.RData"))

# 1. For rejectabc
# Calculating squared relative distances and sum thereof for the ABC rejection method
rej.sum.sq.rel.dist <- rep(0, nrow(rejectabc.output$stats))
for(i in 1:length(target.vector.trainer)) {
  nam <- paste0("y.", i, ".sq.rel.dist")
  val <- ((rejectabc.output$stats[,i] - targets[i]) / targets[i])^2
  assign(nam, val)
  rej.sum.sq.rel.dist <- rej.sum.sq.rel.dist + get(nam)
}

#rejectabc.output$y.1.sq.rel.dist <- ((rejectabc.output$stats[,1] - targets[1]) / targets[1])^2
#rejectabc.output$y.2.sq.rel.dist <- ((rejectabc.output$stats[,2] - targets[2]) / targets[2])^2
#rejectabc.output$sum.sq.rel.dist <- rejectabc.output$y.1.sq.rel.dist + rejectabc.output$y.2.sq.rel.dist
dist.order <- order(rej.sum.sq.rel.dist) # Ordering the squared distances from small to big.
last.one.selected <- 5
selected.distances <- dist.order[1:last.one.selected]
best5.rejection <- rep(FALSE, length(dist.order))
best5.rejection[selected.distances] <- TRUE

abcreject.df <- as.data.frame(cbind(rejectabc.output$param,
                                    rejectabc.output$stats))
abcreject.df$best5 <- best5.rejection
abcreject.df$method <- "rejection"

xvars.names <- paste0("x.", 1:7) # This will also be used by the other methods
yvars.names <- paste0("y.", 1:39) # This will also be used by the other methods
names(abcreject.df) <- c(xvars.names, yvars.names, "best5", "method")




# 2. For Lenormandabc




# 3. For miceabc
# First for the 5 waves
xplusyvars.length <- ncol(MICE_ABC_testoutput$sim.results.with.design[[1]]) - 1 # The last variable is the sum of squared errors
miceabc_inout_all <- do.call(rbind, MICE_ABC_testoutput$sim.results.with.design)[,1:xplusyvars.length]
best5.mice <- miceabc_inout_all$y.1 %in% MICE_ABC_testoutput$inputoutput[[5]]$y.1[1:5]
abcmice.df <- as.data.frame(cbind(miceabc_inout_all,
                                  best5.mice))
abcmice.df$method <- "mice"
names(abcmice.df) <- c(names(miceabc_inout_all), "best5", "method")     ### The dataset abcmice.df will be merged with other datasets generated by the comparison methods

```

Now that we have calibrated the model with Rejection ABC, let's run the 5 best models many times under the intervention and control scenario, to estimate the impact of TasP. 
```{r tasp.incid.rel.reduc.rej}
reps <- 6 # Change to 200 reps eventually
calib.rej.df <- abcreject.df %>% dplyr::filter(., best5 == TRUE) %>% dplyr::select(., x.1:x.7)
design.matrix.calib.rej <- matrix(rep(as.numeric(unlist(calib.rej.df)), each = reps), nrow = reps * nrow(calib.rej.df), byrow = FALSE)
design.matrix.calib.rej.control <- cbind(design.matrix.calib.rej, 0)
design.matrix.calib.rej.interv <- cbind(design.matrix.calib.rej, 1)

summstats.calib.rej.control.df <- simpact.parallel(model = simpact.wrapper.master,
                                  actual.input.matrix = design.matrix.calib.rej.control,
                                  seed_count = 0,
                                  n_cluster = 8)
summstats.calib.rej.interv.df <- simpact.parallel(model = simpact.wrapper.master,
                                  actual.input.matrix = design.matrix.calib.rej.interv,
                                  seed_count = 0,
                                  n_cluster = 8)
lastcolumn.calib.rej <- ncol(summstats.calib.rej.control.df)
incidence.rel.reduc.calib.rej <- (summstats.calib.rej.control.df[,lastcolumn.calib.rej] - summstats.calib.rej.interv.df[,lastcolumn.calib.rej]) / summstats.calib.rej.control.df[,lastcolumn.calib.rej]
hist.data.incidence.rel.reduc.calib.rej <- hist(incidence.rel.reduc.calib.rej, 20)
summary(incidence.rel.reduc.calib.rej)
predict.95.percent.interval.incidence.rel.reduc.calib.rej <- quantile(incidence.rel.reduc.calib.rej, probs = c(0.025, 0.975), na.rm = TRUE)


```









Now that we have calibrated the model with MICE-Cali, let's run the 5 best models many times under the intervention and control scenario, to estimate the impact of TasP. 
```{r tasp.incid.rel.reduc.mice}
reps <- 6 # Change to 200 reps eventually
calib.mice.df <- abcmice.df %>% dplyr::filter(., best5 == TRUE) %>% dplyr::select(., x.1:x.7)
design.matrix.calib.mice <- matrix(rep(as.numeric(unlist(calib.mice.df)), each = reps), nrow = reps * nrow(calib.mice.df), byrow = FALSE)
design.matrix.calib.mice.control <- cbind(design.matrix.calib.mice, 0)
design.matrix.calib.mice.interv <- cbind(design.matrix.calib.mice, 1)

summstats.calib.mice.control.df <- simpact.parallel(model = simpact.wrapper.master,
                                  actual.input.matrix = design.matrix.calib.mice.control,
                                  seed_count = 0,
                                  n_cluster = 8)
summstats.calib.mice.interv.df <- simpact.parallel(model = simpact.wrapper.master,
                                  actual.input.matrix = design.matrix.calib.mice.interv,
                                  seed_count = 0,
                                  n_cluster = 8)
lastcolumn.calib.mice <- ncol(summstats.calib.mice.control.df)
incidence.rel.reduc.calib.mice <- (summstats.calib.mice.control.df[,lastcolumn.calib.mice] - summstats.calib.mice.interv.df[,lastcolumn.calib.mice]) / summstats.calib.mice.control.df[,lastcolumn.calib.mice]
hist.data.incidence.rel.reduc.calib.mice <- hist(incidence.rel.reduc.calib.mice, 20)
summary(incidence.rel.reduc.calib.mice)
predict.95.percent.interval.incidence.rel.reduc.calib.mice <- quantile(incidence.rel.reduc.calib.mice, probs = c(0.025, 0.975), na.rm = TRUE)


```

```{r merging.datasets}
# Adding the target statistics and their inputs
target.df <- data.frame(matrix(c(3, -0.5, 0.5, 5, 3, 3, 0.75, target.vector.trainer), nrow = 1), # The inputs and targets
                        best5 = TRUE, method = "target")
names(target.df) <- c(names(miceabc_inout_all), "best5", "method")


# Now we can rbind these 4 datasets into one dataset that we can plot with ggplot2
abc.comparison.tasp.df <- rbind(abcreject.df,
                           #abcLenorm.df,
                           abcmice.df,
                           target.df)
abc.comparison.tasp.df$method <- factor(abc.comparison.tasp.df$method, labels = c("MICE", "Rejection", "Target")) # c("Lenormand", "MICE", "Rejection", "Target"))

abc.comparison.tasp.df$method <- factor(abc.comparison.tasp.df$method,levels(abc.comparison.tasp.df$method)[c(2, 1, 3)]) # c(3, 1, 2, 4) We want the levels in a particular order, for plotting and colour purposes
#levels(abc.comparison.V8.df$method)

```
Let's plot how the calibrated models compare against the target statistics and eachother 
```{r output.comparison}
# columns 9:24 capture the ART coverage at times 25:40

outputcomparison.data <- as.data.frame(rbind(summstats.calib.rej.interv.df,
                          summstats.calib.mice.interv.df,
                          target.vector.master))
names(outputcomparison.data) <- c(yvars.names, "incid.rel.reduc")
outputcomparison.data$method <- c(rep(c("Rejection", "MICE"), each = nrow(summstats.calib.rej.interv.df)), "Target")

outputcomparison.data$method <- factor(outputcomparison.data$method, labels = c("MICE", "Rejection", "Target")) # c("Lenormand", "MICE", "Rejection", "Target"))

outputcomparison.data$method <- factor(outputcomparison.data$method,levels(outputcomparison.data$method)[c(1, 2, 3)]) # c(3, 1, 2, 4) We want the levels in a particular order, for plotting and colour purposes


outputcomparison.data$is.target <- c(rep(0, nrow(outputcomparison.data)-1), 1)
outputcomparison.data$unique.ID <- as.character(paste0(outputcomparison.data$y.1, outputcomparison.data$y.2, outputcomparison.data$y.3))


###
# Comparing various output statistics
library(GGally)
outputcomparison.data$is.target <- factor(outputcomparison.data$is.target)
ggpairs(outputcomparison.data[, c(1,2,5,6,7, 41:42)],
        aes(colour = method,
            shape = is.target),
        columns = 1:5,
        columnLabels = c("AAD", "SDAD", "WVAD.base", "BVAD", "HIV+ 15-50 yo"),
        upper = list(continuous = "blank")) 

ggpairs(outputcomparison.data[, c(25:30, 33, 36,39, 41:42)],
        aes(colour = method,
            shape = is.target),
        columns = 1:9,
        columnLabels = c("<100 25-30", "<100 30-35", "<100 35-40", "100-200 25-30", "100-200 30-35", "100-200 35-40", "200-350 35-40", "350-500 35-40", ">500 35-40"),
        upper = list(continuous = "blank")) 


# To plot ART coverage over time, we need to turn wide into long format
names(outputcomparison.data)[9:24] <- 25:40
outputcomparison.ARTcoverage.data <- tidyr::gather(data = outputcomparison.data,
                                            key = Time,
                                            convert = TRUE,
                                            value = ART.coverage,
                                            9:24)


ARTcoverage.comparison <- ggplot(data = outputcomparison.ARTcoverage.data,
                      aes(x = Time,
                          y = ART.coverage,
                          alpha = factor(is.target),
                          group = unique.ID,
                          col = method)) +
  geom_line() +
  scale_colour_manual(values = cb.Palette) +
  scale_alpha_discrete(breaks = NULL,
                       range = c(0.2, 1)) +
  #scale_shape_manual(breaks = NULL,
  #                   values = c(20, 10)) +
  #scale_size_manual(breaks = NULL,
  #                  values = 4) +
  xlab("Simulation time (years)") +
  ylab("ART coverage") +
  theme_bw() +
  guides(colour = guide_legend(title = "Method"))#,
                            #   override.aes = list(shape = c(20, 20, 20, 10),
                             #                      size = c(4, 4, 4, 4))))
plot(ARTcoverage.comparison)


### Now let's plot the TasP impact estimate
median.impact <- c(median(incidence.rel.reduc.calib.rej), median(incidence.rel.reduc.calib.mice), median(incidence.rel.reduc, na.rm = TRUE))
mean.impact <- c(mean(incidence.rel.reduc.calib.rej), mean(incidence.rel.reduc.calib.mice), mean(incidence.rel.reduc, na.rm = TRUE))
p25.impact <- c(quantile(incidence.rel.reduc.calib.rej, probs = 0.25, na.rm = TRUE),
                quantile(incidence.rel.reduc.calib.mice, probs = 0.25, na.rm = TRUE),
                quantile(incidence.rel.reduc, probs = 0.25, na.rm = TRUE))
p75.impact <- c(quantile(incidence.rel.reduc.calib.rej, probs = 0.75, na.rm = TRUE),
                quantile(incidence.rel.reduc.calib.mice, probs = 0.75, na.rm = TRUE),
                quantile(incidence.rel.reduc, probs = 0.75, na.rm = TRUE))
p025.impact <- c(quantile(incidence.rel.reduc.calib.rej, probs = 0.025, na.rm = TRUE),
                quantile(incidence.rel.reduc.calib.mice, probs = 0.025, na.rm = TRUE),
                quantile(incidence.rel.reduc, probs = 0.025, na.rm = TRUE))
p975.impact <- c(quantile(incidence.rel.reduc.calib.rej, probs = 0.975, na.rm = TRUE),
                quantile(incidence.rel.reduc.calib.mice, probs = 0.975, na.rm = TRUE),
                quantile(incidence.rel.reduc, probs = 0.975, na.rm = TRUE))
method <- c("Rejection", "MICE", "Master")
impact.comparison.data <- data.frame(median.impact = median.impact,
                                     mean.impact = mean.impact,
                                     p25.impact = p25.impact,
                                     p75.impact = p75.impact,
                                     p025.impact = p025.impact,
                                     p975.impact = p975.impact,
                                     method = method)

impact.comparison <- ggplot(data = impact.comparison.data,
                      aes(x = method,
                          y = median.impact,
                          col = method)) +
  geom_crossbar(aes(ymin = p25.impact, ymax = p75.impact), width = 0.2) +
  geom_errorbar(aes(ymin = p025.impact, ymax = p975.impact), width = 0.2) +
  scale_colour_manual(values = c(cb.Palette[3], cb.Palette[1], cb.Palette[2])) +
  xlab("") +
  ylim(0, 1) +
  ylab("Relative Reduction in HIV incidence") +  # TasP effect on HIV incidence in the last 2 years of the simulation
  theme_bw() +
  guides(colour = guide_legend(title = "Method"))#,
                            #   override.aes = list(shape = c(20, 20, 20, 10),
                             #                      size = c(4, 4, 4, 4))))
plot(impact.comparison)

```



